Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-24 analysis/paper/paper.Rmd
Fix an errant "," and objective statement

Because of the well documented interactions between irrigation and N, we established field experiments to determine what effects AWD and N could have upon ShB incidence and severity in tropical rice.

@@

Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14&deg; 11' N, , longitude 121&deg; 15' E) in the 2015 and 2016 dry seasons. For 2016 changes were made to optimize the experiment based on findings from the 2015 experiment. Details were as follows.

>>>>

Because of the well documented effects of irrigation and N on ShB, we established field experiments to study what effects AWD irrigation technologies and N could have upon ShB incidence and severity in tropical rice.

@@

Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14&deg; 11' N, longitude 121&deg; 15' E) in the 2015 and 2016 dry seasons. For 2016 changes were made to optimize the experiment based on findings from the 2015 experiment. Details were as follows.
